%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alan (Jia Lin) Yuan} \\ \vspace{1pt}
    \small \href{mailto:alan.yuan.jly@gmail.com}{\underline{alan.yuan.jly@gmail.com}} $|$
    \href{https://linkedin.com/in/jalnyn}{\underline{linkedin.com/in/jalnyn}} $|$
    \href{https://github.com/jalnyn}{\underline{github.com/jalnyn}} $|$
    \href{https://scholar.google.com/citations?user=o-YyMz4AAAAJ&hl=en}{\underline{scholar.google.com/}}
\end{center}


%-----------EDUCATION-----------
\vspace{0pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{4.0 cGPA}
      {MSc in Applied Computing (A.I.)}{Sept 2023 -- Dec 2024}

    \resumeSubheading
      {University of Toronto}{3.84 cGPA}
      {HBSc Computer Science Specialist, Major in Mathematics}{Sep. 2018 -- May 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Parallel Programming (A+), Neural Networks and Deep Learning (A+), Algorithm Design, Analysis \& Complexity (A), Operating Systems (A+), Intro to AI (A+)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\vspace{-8pt}
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]
    \item{
    \small{M. Skreta*, Z. Zhou*, \textbf{J. L. Yuan}*, K. Darvish, A. Aspuru-Guzik, A. Garg. RePLan: Robotic Replanning with Perception and Language Models. \textit{arXiv:2401.04157}, 2024.}
    }
    \item{
    \small{M. Mittal, C. Yu, Q. Yu, J. Liu, N. Rudin, D. Hoeller, \textbf{J. L. Yuan}, R. Singh, Y. Guo, H. Mazhar, A. U. Mandlekar, B. Babich, G. State, M. Hutter, A. Garg. ORBIT: A Unified Simulation Framework for Interactive Robot Learning Environments. \textit{IEEE Robotics and Automation Letters (RA-L)}, 2023.}
    }
\end{itemize}


%-----------EXPERIENCE-----------
\vspace{-8pt}
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Instacart}{Feb 2025 -- Present}
      {Software Developer}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Consolidated cross-account/cross-region \textbf{RDS/Aurora} backup lifecycle, saving \textbf{\$1M/year} in AWS costs.}
        \resumeItem{Built automated snapshot restore and validation workflows, enabling proactive detection of unrecoverable backups.}
        \resumeItem{Scaled \textbf{tier 0/1} databases (IOPS, CPU instances, replicas) for holiday peak, resulting in a stable on-call season.}
      \resumeItemListEnd

    \resumeSubheading
      {Unilever}{April 2024 -- Dec 2024}
      {Machine Learning Engineer - Intern}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Trained \textbf{time-series transformer} models to \textbf{forecast sales} with \textbf{PyTorch}, increasing accuracy by 5\%.}
        \resumeItem{\textbf{Optimized promotion times and prices} with augmented genetic algorithms \textbf{GNGSA}.}
        \resumeItem{Utilized novel algorithm \textbf{GNGSA} increasing convergence iterations 70\% and hypervolume AUC by 50\%.}
        \resumeItem{Implemented multi-thread processing to increase data pipeline speeds by \textbf{50\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Jun 2023 -- Aug 2023}
      {Software Developer - Intern}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Designed a \textbf{precompute} layer using \textbf{Apache Spark} to increase recommendation speed by \textbf{99\%} from 150ms.}
        \resumeItem{Built data pipelines to ingest updated data and retrain models on a scheduled basis.}
        \resumeItem{Created automated data analysis tool to ensure predictions are above \textbf{75\%} accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{May 2022 -- Aug 2022}
      {Software Developer - Intern}{Vancouver, British Columbia}
      \resumeItemListStart
        \resumeItem{Engineered a modular microservice in \textbf{Java} to send cashback notifications to customers on select products.}
        \resumeItem{Utilized \textbf{AWS} web services such as \textbf{Lambda}, \textbf{SQS} and \textbf{SNS} to ensure scalability.}
        \resumeItem{Integrated service into data pipeline utilizing Amazon internal language \textbf{Datapath}.}
      \resumeItemListEnd

    \resumeSubheading
      {Intel}{May 2021 -- May 2022}
      {Software Engineer - Intern}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Developed \textbf{C++} \textbf{fuzz testing} tooling generating 4000+ randomized programs to verify compiler correctness against uncompiled execution.}
        \resumeItem{Optimized support tool's RAM templates to reduce false positives and failing cases by around \textbf{70\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {Centivizer}{Apr 2020 -- Sep 2020}
      {Software Developer - Part-time}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Designed backend application using \textbf{Node.JS} and \textbf{SimplePeer} to facilitate \textbf{real-time video streams}.}
        \resumeItem{Integrated video system with main \textbf{React} site and \textbf{NoSQL} database.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\vspace{-8pt}
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{WIDE: Websocket-IDE} $|$ \href{https://github.com/JaLnYn/websocket-ide}{GitHub}}{Sep 2024 -- present}
          \resumeItemListStart
            \resumeItem{Architecting and developing a websocket-based IDE using \textbf{Rust} and \textbf{React} frontend (58 GitHub stars).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Decomposed Face Generation} $|$ \href{https://github.com/JaLnYn/talkinghead}{GitHub}}{Apr 2024 -- Aug 2024}
          \resumeItemListStart
            \resumeItem{Decomposed faces into \textbf{id, pose, emotion embeddings} using \textbf{contrastive learning} approaches.}
            \resumeItem{Developed architecture combining \textbf{StyleGAN} with multiple embedding spaces for controllable generation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{RePlan: Robot Planning with LLMs} $|$ \href{https://arxiv.org/abs/2401.04157}{arXiv:2401.04157}}{Sep 2023 -- Aug 2024}
          \resumeItemListStart
            \resumeItem{Developed novel system combining \textbf{MPC} and \textbf{MultiModal LLM} for completing high-level robot tasks.}
            \resumeItem{Created \textbf{MuJoCo} environments for training and evaluating manipulation policies.}
            \resumeItem{Implemented meta-controllers for \textbf{multi-policy} agents using \textbf{sparse rewards}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MultiModal AI Story Teller} $|$ private repo}{Jul 2023 -- Jul 2024}
          \resumeItemListStart
            \resumeItem{Built interactive \textbf{socket-based} streaming service serving up to 200+ users a day.}
            \resumeItem{Managed \textbf{auto-scaling GPU} resources with \textbf{Kubernetes} saving up to 90\% on \textbf{AWS} costs.}
            \resumeItem{Implemented \textbf{Multimodality} using \textbf{LLMs} and \textbf{Latent Diffusion Models} to build an interactive story teller.}
            \resumeItem{Utilized NLP techniques to summarize context to reduce context size, reducing inference time by up to 10\%.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Orbit: Robot Learning Framework} $|$ \href{https://isaac-orbit.github.io/}{project-site}}{Jan 2022 -- May 2023}
          \resumeItemListStart
            \resumeItem{Core contributor to robotics framework built on \textbf{NVIDIA IsaacSim}, published in \textit{IEEE RA-L}.}
            \resumeItem{Designed \textbf{GPU-accelerated} state systems achieving a \textbf{4x} speedup over CPU solutions.}
            \resumeItem{Implemented \textbf{PPO} training pipelines with \textbf{domain randomization} for manipulation tasks.}
            \resumeItem{Wrote a low-overhead semantics system to represent semantics and physics simulation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CaNetDa: Deep Learning for GeoGuesser in Canada} $|$ \href{https://github.com/st-tran/CSC413-Project}{GitHub}}{Jan 2021 -- Apr 2021}
          \resumeItemListStart
            \resumeItem{Mined dataset and trained an ensemble of \textbf{ResNet}, \textbf{EfficientNet} and \textbf{Vision Transformer} models.}
            \resumeItem{Achieved \textbf{47\%} improvement over random agent in predicting province of image in Canada.}
            \resumeItem{Scraped \textbf{Google Street View} images and used \textbf{Google Maps API} to preprocess images for training.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Deep Q-Learning Snake Agent} $|$ \href{https://github.com/JaLnYn/pokerbot}{GitHub}}{May 2021 -- Dec 2021}
          \resumeItemListStart
            \resumeItem{Utilized \textbf{PyTorch} to write a Deep Q-Learning snake agent reaching a high score of \textbf{40} after \textbf{5} minutes of training.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Tron UDP Multiplayer} $|$ \href{https://github.com/JaLnYn/Tron}{GitHub}}{Sep 2019 -- Dec 2019}
        \resumeItemListStart
          \resumeItem{Created a four-player game for local networks using the \textbf{UDP network protocol} and C\texttt{++}.}
          \resumeItem{Utilized \textbf{epoll} for both client and server to monitor the socket, timer (server) and stdin (client).}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\vspace{-8pt}
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Tech}{: Deep Neural Networks, Large Language Models, Latent Diffusion Models, Reinforcement Learning, Python, C++, JavaScript, Java, Rust} \\
     \textbf{Tools}{: Huggingface, PyTorch, Git, React, Node.js, MongoDB, SQL, Numpy, GraphQL, NVIDIA IsaacSim, MuJoCo, Kubernetes, AWS, Apache Spark} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
