
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Alan Yuan} \\ \vspace{1pt}
    \small \href{mailto:alan.yuan.jly@gmail.com}{\underline{alan.yuan.jly@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jalnyn}{\underline{linkedin.com/in/jalnyn}} $|$
    \href{https://github.com/jalnyn}{\underline{github.com/jalnyn}}
\end{center}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intel}{May 2021 -- Present}
      {Software Engineer - Intern}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Developing Quartus software using \textbf{C\texttt{+}\texttt{+}}, \textbf{Python} and \textbf{Bash} for speedup during synthesis by re-routing the flow.}
        \resumeItem{Developing Quartus support software to generate 4000+ of completely random test-cases for edge-case testing}
        \resumeItem{Optimized support tool's Ram templates to reduce false positives and failing cases by around \textbf{70\%}}
        \resumeItem{Implemented various new features and upgrades such as re-scripting tools to ustilize new control system, dynamic database size notifier, hierarchy re-router for missing entities, automatic parameter setting aggregator and more.}
        \resumeItem{Assisting in migrating all 613 failing regression test cases from pre-existing flow to the new faster flow.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Centivizer}{April 2020 - Sept 2020}
      {Software Developer - Part-time}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Fully designed and wrote backend application using \textbf{Node.JS} and \textbf{SimplePeer} to connect users via Video}
        \resumeItem{Establish communication between client and backend for video feed using socket.io to }
        \resumeItem{Integrated video feature with user database through RESTful API using the Axios Library}
        \resumeItem{Decreased server load by re-working notification system to use a Socket based approach}
    \resumeItemListEnd
   \resumeSubHeadingListEnd

% \section{Other Experiences}
%     \resumeSubheading
%       {PAIR Lab }{Sept 2021 - present}
%       {Lab Assistant - Part-time}{Toronto, Ontario}
%       \resumeItemListStart
%         \resumeItem{Develop randomized scenes for Reinforcement Robot Learning }
%     \resumeItemListEnd

%   \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{3.83 cGPA}
      {BSc Computer Science Specialist, Major in Mathematics}{Sep. 2018 -- May 2023}
            \resumeItem{\textbf{Relevant Coursework}: Data Structures and Algorithms (A+), Operating Systems (A+), Parallel Programming (A+), Neural Networks and Deep Learning (A+), Intro to AI (A+), Introduction to Machine Learning (A+), Algorithm Design, Analysis \& Complexity (A)}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{CFR Minimization (Kuhn Poker, Tic-Tac-Toe and Coup)} $|$ Link: \href{https://github.com/JaLnYn/pokerbot}{GitHub}}{May 2021 -- present}
          \resumeItemListStart
            \resumeItem{Developing a general framework to train R.L. agents using CFR, CFR+ and MCCFR to find the nash equilibrium.}
            \resumeItem{Implemented each of the algorithms to play tic-tac-toe, Kuhn poker and Coup.}
          \resumeItemListEnd


        \resumeProjectHeading
          {\textbf{Tenant-Landlord Matching App} $|$ Links: \href{https://github.com/JaLnYn/pk2_ser}{server-side}, \href{https://github.com/JaLnYn/pk2_cli}{client-side}}{Aug 2020 -- June 2021}
          \resumeItemListStart
            \resumeItem{Fullstack development of an mobile application to match landlords and tenants}
            \resumeItem{Constructed front-end using \textbf{React-native} and common packages such as \textbf{react-navigation} and \textbf{axios}}

            \resumeItem{Leveraged form handler: \textbf{multer} to seperatly handle images upload and download}
            \resumeItem{App includes features: Authentication, Images upload, Property Managment, Profile Matching via swiping and instant messaging utilizing \textbf{Socket.io}}
            \resumeItem{Utilized \textbf{Node.js}, \textbf{GraphQL}, and database \textbf{Postgres} to construct backend.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CaNetDa: Deep learning for GeoGuesser in Canada} $|$ Link: \href{https://github.com/st-tran/CSC413-Project}{GitHub}}{Jan 2021 -- April 2021}
          \resumeItemListStart
            \resumeItem{In this project we used a deep learning approach utilizing multiple deep learning techniques to have an AI play GeoGuesser. GeoGuesser is a game where players guess the location of a street view image.}
            \resumeItem{Utilized \textbf{ResNet}, \textbf{EfficientNet} and \textbf{Vision Transformer} to predict the location}
            \resumeItem{With our approach, a accuracy of \textbf{60\%} was consistently achieved.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Tron UDP multiplayer} $|$ Link: \href{https://github.com/JaLnYn/Tron}{GitHub}}{Sep 2019 -- Dec 2019}
          \resumeItemListStart
            \resumeItem{Tron is a game where four players move around the grid leaving a trail behind. Any player running into a trail is eliminated. Last person standing wins.}
            \resumeItem{Created a four player game for local networks using the UDP network protocol and C++}
            \resumeItem{Forked timer from the server to ensure the game runs on time}
            \resumeItem{Utilize epoll for both client and server to monitor the socket as well as the timer (server) and stdin (client)}
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL (Postgres), JavaScript, Java, C\#, R} \\
     \textbf{Tools}{: Git, React-Native, Node.js, MongoDB, MySQL, PyTorch, Numpy, Pandas} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}

